Verifying Demonstrations

### 2018-11-13 paper/DB-anon-cred.tex

One protocol exists in the literature that provides \acp{PPK} with most of the 
desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
  shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} 
protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of 
anonymous credentials whose desirable properties we list in
\cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation. 
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

@@

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the 
distance-bounding protocols is based on the Schnorr identification 
scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \ac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
It is important in our setting that the protocol is a public-key protocol, this 
property implies protection against an impersonating verifiers.

@@

During one round, the prover commits to a random nonce: \ie chooses 
\(\rho\rgets \ZZ_q\) uniformly randomly, computes \(R\gets g^\rho\) and sends 
\(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) 
and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This is the main difference to the original Schnorr protocol: the verifier 
selects two challenges and the prover computes two responses --- but still only 
\emph{one nonce}, \(\rho\).
(This is also different from Brands-Chaum, where the prover and verifier 
jointly construct \emph{one} challenge with \emph{one} response.)

@@

The prover must know the responses for both challenges to successfully pass the 
\ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the 
responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH},
and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the 
\(l\) bits the verifier must learn of \(s_{1-b}\):
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with 
secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus we still have information theoretic security for \(s_{1-b}\) although we 
reveal the \(l\) bits.

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
none of the other --- only \(l\leq |q|\) bits of \emph{one of two} information 
theoretically independent \(|q|\)-bit shares.
The adversary now has two options.
First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat 
  s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
However, at this point the adversary must wait for the challenge bit 
\(b_{l+1}\) from the verifier and then relay that challenge to the prover to 
receive the correct \(r_i\) --- this relay will be detected.
The alternative is to guess \(b\) and extract \(s_b\) for this challenge from 
the prover.
Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will 
guess it correctly.
Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
The adversary can also guess the remaining \(2|q|-l\) bits, which we will 
discuss more below.
The probability of guessing these bits successfully is \(2^{-(2|q|-l)}\).
However, \(l < |q| \implies 2|q|-l > |q|\) and this might thus be more 
expensive than guessing \(s_{1-b}\) directly, which is \(2^{-|q|}\).
Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
\(2^{-n}+2^{-|q|n}\).

The protocol is \ac{DBTF}-resistant, indeed, if the malicious prover gives both 
responses to the accomplice, the accomplice can compute his secret key.
The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie 
\(1/2\) per round or, in total, \(2^{-n}\).

The protocol is also secure against distance hijacking due to the fact
that it is the authenticating bitstring that is used during the \ac{DB}
phase, not the challenge bitstring as in the protocol of Brands-Chaum.

@@

We wanted to formally verify the protocol security properties. We used the Tamarin prover ~\cite{meier2013tamarin}. Tamarin does not include timestamp and location data in its model, but thanks to the work by Mauw \emph{et al.}~\cite{TamarinDB}, we know that all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modelization choices we made. It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true. We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.

>>>>

One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation. 
To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.

@@

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.

@@

During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
This is also different from the original Brands-Chaum protocol, in which the prover and verifier jointly construct \emph{one} challenge with \emph{one} response.)

@@

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but none of the other --- only \(l\leq |q|\) bits of \emph{one of two} information theoretically independent \(|q|\)-bit shares.
Now, the adversary has two options.
First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
The adversary can also guess the remaining \(2|q|-l\) bits, which we will discuss in more details below.
The probability of guessing these bits successfully is \(2^{-(2|q|-l)}\).
However, \(l < |q| \implies 2|q|-l > |q|\) and this might thus be more expensive than guessing \(s_{1-b}\) directly, which is \(2^{-|q|}\).
Thus the success probability of the \ac{DBMF} adversary is \emph{at most} \(2^{-n}+2^{-|q|n}\).

The protocol is \ac{DBTF}-resistant. 
Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).

The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.

@@

We wanted to formally verify the protocol security properties. 
To realize this, we used the Tamarin prover ~\cite{meier2013tamarin}. 
Tamarin does not include originally the possibility to reason on time and space in its model.
However, thanks to a recent work by Mauw and co-authors~\cite{TamarinDB}, all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
We are currently investigating the Tamarin interactive mode to validate as well the security properties.

### 2018-11-13 paper/ZKPK.tex

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.

>>>>

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.

### 2018-11-13 paper/adversary-model.tex

One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as \ac{Tor}, for anonymous communication.
However, given a strong enough adversary, such anonymous communication might not be possible.
We capture such a strong adversary in the following definition.

@@

The base rationale is the same as for \cref{base-identity-cause-adversary}, the 
witness \(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
Anyone who is in the same location will learn that \(W\) was present, we want 
to prevent anyone \emph{not present} to learn that \(W\) was there --- hence we 
do not consider the protester as part of the adversary, only \(S\).
Analogous to the identity--cause adversary, we conclude with the strongest 
identity--location adversary.

>>>>

One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous communication.
However, given a strong enough adversary, such anonymous communication might not be possible.
We capture such a strong adversary in the following definition.

@@

The base rationale is the same as for \cref{base-identity-cause-adversary}, the 
witness \(W\) can submit to \(S\) over an anonymous channel, such as Tor~\cite{Tor}.
Anyone who is in the same location will learn that \(W\) was present, we want 
to prevent anyone \emph{not present} to learn that \(W\) was there --- hence we 
do not consider the protester as part of the adversary, only \(S\).
Analogous to the identity--cause adversary, we conclude with the strongest 
identity--location adversary.

### 2018-11-13 paper/analysis-performance.tex

\section{Performance and implementation}
\label{PerformanceAnalysis}

Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and
computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
The first step is only done once and is fairly costly in terms of ressources. 
This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
This can be reduced to 4 random number generations and one exponentiation using precomputation.
The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.
%[2] Lee, M., Dunn, A., Katz, J., Waters, B., & Witchel, E. (2013). Anon-pass: Practical anonymous
%subscriptions. IEEE Security & Privacy, (1), 1.

@@

>>>>

\section{Performance and implementation}
\label{PerformanceAnalysis}
\sonja{ Include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}

\subsection{Smartphones, smartcards}
Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

\subsection{Distance bounding anonymous credentials}
With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. The first step is only done once and is fairly costly in terms of ressources. 
This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
This can be reduced to 4 random number generations and one exponentiation using precomputation. The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.
%[2] Lee, M., Dunn, A., Katz, J., Waters, B., & Witchel, E. (2013). Anon-pass: Practical anonymous
%subscriptions. IEEE Security & Privacy, (1), 1.

@@

\subsection{Ledger (blockchain) efficiency}
As an example, consider a protest with 1\,000\,000 participants.
If we use trusted witnesses, each participant only needs to acquire one proof share from a trusted witness.
Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
If we consider OmniLedger~\cite{OmniLedger}, which can do approximately 1500 transactions per second, it takes at least 11 minutes to process all the proof shares.

If we do not use trusted witnesses, but a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. While this already takes longer than counting votes in national elections, the threshold is still very low. Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. In addition to the ledger computation, we need to consider the creation of the proof shares. \sonja{added the previous sentence to explain why anonpass shows up here. Shouldn't that be in the performance section? }
According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
This yields \(
  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
  \SI{48}{\second}.
\) of processing. For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. Considering that online forums can facilitate mass coordination, the threshold approach seems not only inefficient but also potentially ineffective for verifiability.

%\subsection{Blockchain efficiency}

\sonja{removed for now: One problem can arise in the case in which there is no trusted witnesses.
In this situation, if we set the threshold too high, we need to submit more proof shares than the blockchain can handle within a reasonable time.}

%assumptions about smartphones:
%(This means that we essentially provide a lower bound for the participation 
%count, since some participants might not have such a device.)
%Sonja says: is this still true? Given mafia fraud we can't guarantee
%that, right?

### 2018-11-13 paper/privacy-properties.tex

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
\daniel{%
  No, that implication is not true, counter example:
  There is receipt freeness for how a elector voted, but not that they voted.
  As Simon pointed out, they tick me off, so it's visible that I've voted.
  But no one will ever know for which party I voted.%
}

@@

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}
Finally, any temporary identifiers such as pseudonyms should only be reused when strictly necessary for the fulfillment of verifiability properties listed in \label{verifiability-properties} to prevent inference on long-term identities by repeated samples and side information.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every participant's real (long-term) identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) must be unlinkable between protesters. (\(\pid, \pid' \))
\end{requirements}

>>>>

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
\daniel{%
  No, that implication is not true, counter example:
  There is receipt freeness for how an elector voted, but not that they voted.
  As Simon pointed out, they tick me off, so it's visible that I've voted.
  But no one will ever know for which party I voted.%
}

@@

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}
Finally, any temporary identifiers such as pseudonyms should only be reused 
when strictly necessary for the fulfillment of verifiability properties listed 
in \cref{verifiability-properties} to prevent inference on long-term identities 
by repeated samples and side information.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every 
  participant's (protester and witness) real (long-term) identity (\(P\)) must 
  be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) must be unlinkable between protesters. (\(\pid, \pid' \))
\end{requirements}

### 2018-11-13 paper/system-model.tex

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation.

In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries in terms of the computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is necessary at that time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.
%\sonja{another place to put reasons? Or if here, then for all
%  assumptions. ``We need global connectivity before to read the head from the blockchain.
%We need global connectivity after to upload the proof shares to the blockchain.''}

@@

We consider two types of adversaries: \begin{enumerate*} \item an honest-but-curious adversary
of up to national scale representing a government that can observe any
messages sent, and \item a malicious adversary that can control a
minority of 
equipment such as participants' or witnesses' smartphones or servers
used for the ledger such as miners for a blockchain. \end{enumerate*}

>>>>

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation\footnote{
Of course, this has for consequence that the \ac{CA} can perform a Sybil attack on the system.
Thus, if the \ac{CA} is controlled by the government, no counts in favor of the government can be be trusted.
}.

In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries in terms of the computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is necessary at that time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.

@@

We consider two types of adversaries: 
\begin{enumerate*} 
\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
\end{enumerate*}
